%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PlushCV - One Page Two Column Resume
% LaTeX Template
% Version 1.0 (11/28/2021)
%
% Author:
% Shubham Mazumder (http://mazumder.me)
%
% Hacked together from:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Figure out a smoother way for the document to flow onto the next page.
% 3. Add more icon options 
% 4. Fix hacky left alignment on contact line
% 5. Remove Hacky fix for awkward extra vertical space
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the vertical limit.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Icons:
%%Main: https://icons8.com/icons/carbon-copy
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{plushcv}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{ \fontsize{40}{50}\selectfont Alex (Zian)}{ \fontsize{40}{50}\selectfont Wang} 
{\normalsize Software Engineer Intern}
{\contactline{{Vancouver,BC}}
{\href{https://github.com/wza2479110}{\normalsize Alex Wang}}
{\href{https://www.linkedin.com/in/alexzianwang/}{ \normalsize Alex Wang}}
{\href{mailto:wza2479110@gmail.com}{ \normalsize wza2479110@gmail.com}}
{\href{tel:+16043698366}{(604)-369-8366}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.65 \textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{ZL EOR Chemicals Ltd.}
\descript{|Web Developer Intern}
\location{February 2023 - July 2023 | Vancouver, BC}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\sectionsep
\item Utilized \textbf{JavaScript} and \textbf{HTML/CSS} to maintain and update the company website, ensuring accurate information and seamless functionality.
\item Provided technical support for website issues, showcasing problem-solving skills.
\item Managed website content, including updating new context into existing information.
\item Collaborated with the IT team to implement improvements and troubleshoot issues, utilizing \textbf{Git} for efficient workflow management.
\end{tightemize}
\sectionsep

\runsubsection{Crabro Restaurant}
\descript{|Executive Chef}
\location{May 2017 - May 2019 | Burnaby, BC}
\begin{tightemize}
\sectionsep
\item Developed and implemented efficient workflows, similar to optimizing processes in software development.
\item Managed multiple tasks in a fast-paced environment, demonstrating multitasking skills.
\item Fostered a positive team environment, promoting a culture of recognition and motivation.
\end{tightemize}

% \runsubsection{Alexander College}
% \descript{|Front Desk Receptionist}
% \location{April 2016 - August 2016 | Burnaby, BC}
% \begin{tightemize}
% \sectionsep
% \item Provided excellent customer service and addressed inquiries promptly.
% \item Maintained clear communication with students, staff, and faculty.
% \item Quickly resolved front desk issues, demonstrating problem-solving abilities.
% \end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{BCIT Assignment Tracker}
\descript{| React }
\location{May 2023 | COMP3015, BCIT}
\begin{tightemize}
\item Developed a React app for tracking BCIT assignments with features for adding, deleting, and marking as completed.
\item Ensured the Create button functionality was disabled when the input field was empty, enhancing user experience.
\item Utilized React state management to dynamically update the assignment list and track the number of created and completed assignments.
\item Integrated react-icons library for UI enhancements and implemented conditional rendering for assignment status.
\item Conducted thorough testing to ensure all features worked as expected and improved overall application performance.
\end{tightemize}
\sectionsep

\runsubsection{ Web Application Project}
\descript{| PHP}
\location{March 2023 | COMP3015, BCIT}
\begin{tightemize}
\item Developed a PHP, MySQL, and JavaScript web app for user registration, login, and article management.
\item Implemented secure authentication and parameterized queries to prevent SQL injection.
\item Designed a responsive user interface with HTML/CSS.
\item Managed user profiles with upload functionalities.
\item Conducted thorough testing and debugging.
\end{tightemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Certifications:} 
\begin{tabular}{rll}
2024	     & AWS Academy Graduate - AWS Academy Cloud Architecting\\
2022	     & Computer System Certificate (BCIT)\\
\end{tabular}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.36\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PORTFOLO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Portfolo} 
\descript{An aspiring Computer System undergraduate with a keen interest in developing innovative software solutions. familiar with data structure and algorithms, experienced in web development with different languages Demonstrates a strong foundation in problem-solving and a collaborative approach to working with cross-functional teams.}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{SKILLS}
\subsection{LANGUAGES}
\sectionsep 
Javascript \textbullet{} PHP Laravel \textbullet{} Java \textbullet{} Python \textbullet{} C++ \textbullet{}  C\# \textbullet{} SQL \textbullet{} React \textbullet{} Swift \textbullet{} CSS \\
\sectionsep
\subsection{OS}
\sectionsep
Windows \textbullet{} Linux \textbullet{} Mac \\
\sectionsep
\sectionsep
\subsection{Software/Tools}
\sectionsep
Crystal Report \textbullet{} IntelliJ \textbullet{} Visual Studio Code  \\ \textbullet{} Figma  \textbullet{}  Git \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{British Columbia \\Institute of Technology (BCIT)}
\descript{Computer Systems Diploma}
\location{Expected September 2024 | Burnaby, Canada}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\begin{tightemize}
\sectionsep
\item C\# Application Development
\item SAP Crystal Reports
\item Front-End Web Dev with React
\item Web App Development with PHP
\item iOS Mobile App Development
\item Algorithm Analysis and Design
\item Computer Networking
\item Agile Scrum Framework
\item UX/UI Design
\item Programming with Python
\item Web Development JavaScript
\item AWS Academy Cloud Architecting
\item Relational Database \& SQL

\end{tightemize}
\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}

